Relative Photometry of HD 227858 and HD 338931 from Landholt Standard SA 113475

### 2013-12-06 paper.tex
updated vals for signal

\section{Analysis}
$S_{*,sky}=\Delta\nu{\obar{\Phi}}{\obar{f}}tA/g$
\begin{tabular}{c | c | c | c | c}
Star & Filter & X & $S_{*,sky}$ & $S_{sky}$ \\
\hline
HD 227858 & B & & 668721.3 & 1088003.27\\
HD 227858 & I & & 503371.8 & 427838.5534\\
HD 227858 & R & & 669765.3 & 1028251.386\\
HD 227858 & V & & 396151.3 & 700931.7268\\
HD 338931 & B & & 1118167 & 463203.7293\\
HD 338931 & I & & 1021443 & 422439.6612\\
HD 338931 & R & & 1062403 & 1035817.766\\
HD 338931 & V & & 567930 & 708921.9555\\
SA 113475 & B & & 139874.2 & 479501.2852\\
SA 113475 & I & & 461871.4 & 678267.3456\\
SA 113475 & R & & 643029.1 & 1699412.832\\
SA 113475 & V & & 367109.7 & 1110109.973\\
SA 113475 & B & & 565539.5 & 1492937.888\\
SA 113475 & I & & 1992206 & 4536981.855\\
SA 113475 & R & & 250266.8 & 626392.1272\\
SA 113475 & V & & 318196.8 & 983429.69\\
\end{tabular}

>>>>

\begin{tabular}{c | c | c | c | c}
Star & Filter & $X=\sec{z}$ & $S_{*,sky}$ & $S_{sky}$ \\
\hline
HD 227858 & B & 1.147 & 549081 & 445607 \\
HD 227858 & I & 1.156 & 437742 &  182394\\
HD 227858 & R & 1.152 & 551039 & 438748\\
HD 227858 & V & 1.150 & 320125 & 282855\\
HD 338931 & B & 1.188 & 1078502 & 286905\\
HD 338931 & I & 1.197 & 982646 & 254194\\
HD 338931 & R & 1.194 & 996322 & 632289\\
HD 338931 & V & 1.191 & 526991 & 443543\\
SA 113475 & B & 1.150 & 139874 & 128880\\
SA 113475 & I & 1.153 & 461871 & 186586\\
SA 113475 & R & 1.151 & 643233 & 440040\\
SA 113475 & V & 1.151 & 367110 & 294031\\
SA 113475 & B & 1.428 & 565220 & 403841\\
SA 113475 & I & 1.475 & 1991118 & 1138438\\
SA 113475 & R & 1.454 & 251570 & 148624\\
SA 113475 & V & 1.441 & 318197 & 264164
\end{tabular}

\section{Analysis}
$S_{*,sky}=\Delta\nu{\obar{\Phi}}{\obar{f}}tA/g$
